Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-18 cordillera-cycle.tex
Typeset: pull typesetted references.

\bibliographystyle{copernicus}
\bibliography{refs/references}
\newpage

>>>>

\begin{thebibliography}{114}

\bibitem[{Albrecht et~al.(2011)Albrecht, Martin, Haseloff, Winkelmann, and
  Levermann}]{Albrecht.etal.2011}
 Albrecht,~T., Martin,~M., Haseloff,~M., Winkelmann,~R., and Levermann,~A.: Parameterization for subgrid-scale motion of ice-shelf calving fronts, The Cryosphere, 5, 35--44,
doi:\href{http://dx.doi.org/10.5194/tc-5-35-2011}{10.5194/tc-5-35-2011}, 2011.

\bibitem[{Amante and Eakins(2009)}]{Amante.Eakins.2009}
Amante,~C. and Eakins,~B.~W.: ETOPO1 1 arc-minute global relief model: procedures, data sources and analysis, NOAA technical memorandum NESDIS NGDC-24, Natl. Geophys. Data Center, NOAA, Boulder, CO,
doi:\href{http://dx.doi.org/10.7289/V5C8276M}{10.7289/V5C8276M}, 2009.

\bibitem[{Andersen et~al.(2004)Andersen, Azuma, Barnola, Bigler, Biscaye, Caillon, Chappellaz, Clausen, Dahl-Jensen, Fischer, Fl\"uckiger, Fritzsche, Fujii, Goto-Azuma, Gr{\o}nvold, Gundestrup, Hansson, Huber, Hvidberg, Johnsen, Jonsell, Jouzel, Kipfstuhl, Landais, Leuenberger, Lorrain, Masson-Delmotte, Miller, Motoyama, Narita, Popp, Rasmussen, Raynaud, Rothlisberger, Ruth, Samyn, Schwander, Shoji, Siggard-Andersen, Steffensen, Stocker, Sveinbj\"ornsd\'ottir, Svensson, Takata, Tison, Thorsteinsson, Watanabe, Wilhelms, and White}]{Andersen.etal.2004}
Andersen,~K.~K., Azuma,~N., Barnola,~J.-M., Bigler,~M., Biscaye,~P., Caillon,~N., Chappellaz,~J., Clausen,~H.~B., Dahl-Jensen,~D., Fischer,~H., Fl\"uckiger,~J., Fritzsche,~D., Fujii,~Y., Goto-Azuma,~K., Gr{\o}nvold,~K., Gundestrup,~N.~S., Hansson,~M., Huber,~C., Hvidberg,~C.~S., Johnsen,~S.~J., Jonsell,~U., Jouzel,~J., Kipfstuhl,~S., Landais,~A., Leuenberger,~M., Lorrain,~R., Masson-Delmotte,~V., Miller,~H., Motoyama,~H., Narita,~H., Popp,~T., Rasmussen,~S.~O., Raynaud,~D., Rothlisberger,~R., Ruth,~U., Samyn,~D., Schwander,~J., Shoji,~H., Siggard-Andersen,~M.-L., Steffensen,~J.~P., Stocker,~T., Sveinbj\"ornsd\'ottir,~A.~E., Svensson,~A., Takata,~M., Tison,~J.-L., Thorsteinsson,~T., Watanabe,~O., Wilhelms,~F., and White,~J.~W.~C.: High-resolution record of Northern Hemisphere climate extending into the last interglacial period, Nature, 431, 147--151,
doi:\href{http://dx.doi.org/10.1038/nature02805}{10.1038/nature02805}, data archived at the World Data Center for Paleoclimatology, Boulder, Colorado, USA, 2004.

\bibitem[{Aschwanden et~al.(2012)Aschwanden, Bueler, Khroulev, and Blatter}]{Aschwanden.etal.2012}
Aschwanden,~A., Bueler,~E., Khroulev,~C., and Blatter,~H.: An enthalpy formulation for glaciers and ice sheets,~J. Glaciol., 58, 441--457,
doi:\href{http://dx.doi.org/10.3189/2012JoG11J088}{10.3189/2012JoG11J088}, 2012.

\bibitem[{Aschwanden et~al.(2013)Aschwanden, A{\dh}algeirsd\'{o}ttir, and Khroulev}]{Aschwanden.etal.2013}
 Aschwanden,~A., A{\dh}algeirsd\'{o}ttir,~G., and Khroulev,~C.: Hindcasting to measure ice sheet model sensitivity to   initial states, The Cryosphere, 7, 1083--1093,
doi:\href{http://dx.doi.org/10.5194/tc-7-1083-2013}{10.5194/tc-7-1083-2013}, 2013.

\bibitem[{Balay et~al.(2015)Balay, Abhyankar, Adams, Brown, Brune, Buschelman, Eijkhout, Gropp, Kaushik, Knepley, McInnes, Rupp, Smith, and Zhang}]{Balay.etal.2015}
Balay,~S., Abhyankar,~S., Adams,~M.~F., Brown,~J., Brune,~P., Buschelman,~K.,
Eijkhout,~V., Gropp,~W.~D., Kaushik,~D., Knepley,~M.~G., McInnes,~L.~C.,
Rupp,~K., Smith,~B.~F., and Zhang,~H.: {PETS}c {W}eb page, available at:
\url{http://www.mcs.anl.gov/petsc} (last access: 2015), 2015.

\bibitem[{Barendregt and Irving(1998)}]{Barendregt.Irving.1998}
Barendregt,~R.~W. and Irving,~E.: Changes in the extent of North American ice sheets during the late Cenozoic, Can.~J. Earth Sci., 35, 504--509,
doi:\href{http://dx.doi.org/10.1139/e97-126}{10.1139/e97-126}, 1998.

\bibitem[{Bednarski and Smith(2007)}]{Bednarski.Smith.2007}
Bednarski,~J.~M. and Smith,~I.~R.: Laurentide and montane glaciation along the Rocky Mountain Foothills of northeastern British Columbia, Can.~J. Earth Sci., 44, 445--457,
doi:\href{http://dx.doi.org/10.1139/e06-095}{10.1139/e06-095}, 2007.

\bibitem[{Blackwell and Richards(2004)}]{Blackwell.Richards.2004}
Blackwell,~D.~D. and Richards,~M.: Geothermal Map of North America, Am. Assoc. Petr. Geol., Tulsa, OK, 2004.

\bibitem[{Booth et~al.(2003)Booth, Troost, Clague, and Waitt}]{Booth.etal.2003}
Booth,~D.~B., Troost,~K.~G., Clague,~J.~J., and Waitt,~R.~B.: The Cordilleran ice sheet, in: The Quaternary Period in the United States, edited by: Gillespie,~A., Porter,~S., and Atwater,~B., vol.~1 of Dev. Quaternary Sci., Elsevier, Amsterdam, 17--43,
doi:\href{http://dx.doi.org/10.1016/s1571-0866(03)01002-9}{10.1016/s1571-0866(03)01002-9}, 2003.

\bibitem[{Boulton and Clark(1990)}]{Boulton.Clark.1990}
Boulton,~G.~S. and Clark,~C.~D.: A highly mobile Laurentide ice sheet revealed by satellite images of glacial lineations, Nature, 346, 813--817,
doi:\href{http://dx.doi.org/10.1038/346813a0}{10.1038/346813a0}, 1990.

\bibitem[{Boulton et~al.(2001)Boulton, Dongelmans, Punkari, and Broadgate}]{Boulton.etal.2001}
Boulton,~G.~S., Dongelmans,~P., Punkari,~M., and Broadgate,~M.: Palaeoglaciology of an ice sheet through a glacial cycle: the European ice sheet through the Weichselian, Quaternary Res., 20, 591--625,
doi:\href{http://dx.doi.org/10.1016/s0277-3791(00)00160-8}{10.1016/s0277-3791(00)00160-8}, 2001.

\bibitem[{Briner and Kaufman(2008)}]{Briner.Kaufman.2008}
Briner,~J.~P. and Kaufman,~D.~S.: Late Pleistocene mountain glaciation in Alaska: key chronologies,~J. Quaternary Sci., 23, 659--670,
doi:\href{http://dx.doi.org/10.1002/jqs.1196}{10.1002/jqs.1196}, 2008.

\bibitem[{Bueler and Brown(2009)}]{Bueler.Brown.2009}
Bueler,~E. and Brown,~J.: Shallow shelf approximation as a ``sliding law'' in a~thermodynamically coupled ice sheet model,~J. Geophys. Res., 114, F03008,
doi:\href{http://dx.doi.org/10.1029/2008JF001179}{10.1029/2008JF001179}, 2009.

\bibitem[{Bueler and van Pelt(2015)}]{Bueler.Pelt.2015}
 Bueler,~E. and van~Pelt,~W.: Mass-conserving subglacial hydrology in the Parallel Ice Sheet Model version 0.6, Geosci. Model Dev., 8, 1613--1635,
doi:\href{http://dx.doi.org/10.5194/gmd-8-1613-2015}{10.5194/gmd-8-1613-2015}, 2015.

\bibitem[{Bueler et~al.(2007)Bueler, Lingle, and Brown}]{Bueler.etal.2007}
Bueler,~E., Lingle,~C.~S., and Brown,~J.: Fast computation of a viscoelastic deformable Earth model for ice-sheet simulations, Ann. Glaciol., 46, 97--105,
doi:\href{http://dx.doi.org/10.3189/172756407782871567}{10.3189/172756407782871567}, 2007.

\bibitem[{Burke et~al.(2012{\natexlab{a}})Burke, Brennand, and Perkins}]{Burke.etal.2012}
Burke,~M.~J., Brennand,~T.~A., and Perkins,~A.~J.: Transient subglacial hydrology of a thin ice sheet: insights from the Chasm esker, British Columbia, Canada, Quaternary Res., 58, 30--55,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2012.09.004}{10.1016/j.quascirev.2012.09.004}, 2012{\natexlab{a}}.

\bibitem[{Burke et~al.(2012{\natexlab{b}})Burke, Brennand, and Perkins}]{Burke.etal.2012a}
Burke,~M.~J., Brennand,~T.~A., and Perkins,~A.~J.: Evolution of the subglacial hydrologic system beneath the rapidly decaying Cordilleran Ice Sheet caused by ice-dammed lake drainage: implications for meltwater-induced ice acceleration, Quaternary Res., 50, 125--140,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2012.07.005}{10.1016/j.quascirev.2012.07.005}, 2012{\natexlab{b}}.

\bibitem[{Calov and Greve(2005)}]{Calov.Greve.2005}
Calov,~R. and Greve,~R.: A~semi-analytical solution for the positive degree-day model with stochastic temperature variations,~J. Glaciol., 51, 173--175,
doi:\href{http://dx.doi.org/10.3189/172756505781829601}{10.3189/172756505781829601}, 2005.

\bibitem[{Carlson and Clark(2012)}]{Carlson.Clark.2012}
Carlson,~A.~E. and Clark,~P.~U.: Ice sheet sources of sea level rise and
freshwater discharge during the last deglaciation, Rev. Geophys., 50, RG4007,
doi:\href{http://dx.doi.org/10.1029/2011rg000371}{10.1029/2011rg000371},
2012.

\bibitem[{Carrara et~al.(1996)Carrara, Kiver, and Stradling}]{Carrara.etal.1996}
Carrara,~P.~E., Kiver,~E.~P., and Stradling,~D.~F.: The southern limit of Cordilleran ice in the Colville and Pend Oreille valleys of northeastern Washington during the Late Wisconsin glaciation, Can.~J. Earth Sci., 33, 769--778,
doi:\href{http://dx.doi.org/10.1139/e96-059}{10.1139/e96-059}, 1996.

\bibitem[{Clague et~al.(1980)Clague, Armstrong, and Mathews}]{Clague.etal.1980}
Clague,~J., Armstrong,~J., and Mathews,~W.: Advance of the late Wisconsin Cordilleran Ice Sheet in southern British Columbia since 22\,000~yr~BP, Quaternary Res., 13, 322--326,
doi:\href{http://dx.doi.org/10.1016/0033-5894(80)90060-5}{10.1016/0033-5894(80)90060-5}, 1980.

\bibitem[{Clague(1981)}]{Clague.1981}
Clague,~J.~J.: Late Quaternary Geology and Geochronology of British Columbia Part 2: Summary and Discussion of Radiocarbon-Dated Quaternary History, Geol. Surv. of Can., Ottawa, ON, Paper 80-35,
doi:\href{http://dx.doi.org/10.4095/119439}{10.4095/119439}, 1981.

\bibitem[{Clague(1985)}]{Clague.1985}
Clague,~J.~J.: Delaciation of the Prince Rupert -- Kitimat area, British Columbia, Can.~J. Earth Sci., 22, 256--265,
doi:\href{http://dx.doi.org/10.1139/e85-022}{10.1139/e85-022}, 1985.

\bibitem[{Clague(1986)}]{Clague.1986}
Clague,~J.~J.: The Quaternary stratigraphic record of British Columbia --- evidence for episodic sedimentation and erosion controlled by glaciation, Can.~J. Earth Sci., 23, 885--894,
doi:\href{http://dx.doi.org/10.1139/e86-090}{10.1139/e86-090}, 1986.

\bibitem[{Clague(1989)}]{Clague.1989}
Clague,~J.~J.: Character and distribution of Quaternary deposits (Canadian Cordillera), in: Quaternary Geology of Canada and Greenland, edited by: Fulton,~R.~J., vol.~1 of Geology of Canada, Geol. Surv. of Can., Ottawa, ON, 34--48,
doi:\href{http://dx.doi.org/10.4095/127905}{10.4095/127905}, 1989.

\bibitem[{Clague and James(2002)}]{Clague.James.2002}
Clague,~J.~J. and James,~T.~S.: History and isostatic effects of the last ice sheet in southern British Columbia, Quaternary Res., 21, 71--87,
doi:\href{http://dx.doi.org/10.1016/s0277-3791(01)00070-1}{10.1016/s0277-3791(01)00070-1}, 2002.

\bibitem[{Clague and Ward(2011)}]{Clague.Ward.2011}
Clague,~J.~J. and Ward,~B.: Pleistocene Glaciation of British
Columbia, in:   Dev. Quaternary Sci., vol.~15, edited by: Ehlers,~J., Gibbard,~P.~L., and Hughes,~P.~D., Elsevier, Amsterdam, 563--573,
doi:\href{http://dx.doi.org/10.1016/b978-0-444-53447-7.00044-1}{10.1016/b978-0-444-53447-7.00044-1}, 2011.

\bibitem[{Clague et~al.(1997)Clague, Mathewes, Guilbault, Hutchinson, and Ricketts}]{Clague.etal.1997}
Clague,~J.~J., Mathewes,~R.~W., Guilbault,~J.-P., Hutchinson,~I., and Ricketts,~B.~D.: Pre-Younger Dryas resurgence of the southwestern margin of the Cordilleran ice sheet, British Columbia, Canada, Boreas, 26, 261--278,
doi:\href{http://dx.doi.org/10.1111/j.1502-3885.1997.tb00855.x}{10.1111/j.1502-3885.1997.tb00855.x}, 1997.

\bibitem[{Clague et~al.(2005)Clague, Froese, Hutchinson, James, and Simon}]{Clague.etal.2005}
Clague,~J.~J., Froese,~D., Hutchinson,~I., James,~T.~S., and Simon,~K.~M.: Early growth of the last Cordilleran ice sheet deduced from glacio-isostatic depression in southwest British Columbia, Canada, Quaternary Res., 63, 53--59,
doi:\href{http://dx.doi.org/10.1016/j.yqres.2004.09.007}{10.1016/j.yqres.2004.09.007}, 2005.

\bibitem[{Clark and Mix(2002)}]{Clark.Mix.2002}
Clark,~P.~U. and Mix,~A.~C.: Ice sheets and sea level of the Last Glacial Maximum, Quaternary Res., 21, 1--7,
doi:\href{http://dx.doi.org/10.1016/s0277-3791(01)00118-4}{10.1016/s0277-3791(01)00118-4}, 2002.

\bibitem[{Clason et~al.(2012)Clason, Mair, Burgess, and Nienow}]{Clason.etal.2012}
Clason,~C., Mair,~D.~W., Burgess,~D.~O., and Nienow,~P.~W.: Modelling the delivery of supraglacial meltwater to the ice/bed interface: application to southwest Devon Ice Cap, Nunavut, Canada,~J. Glaciol., 58, 361--374,
doi:\href{http://dx.doi.org/10.3189/2012jog11j129}{10.3189/2012jog11j129}, 2012.

\bibitem[{Clason et~al.(2014)Clason, Applegate, and Holmlund}]{Clason.etal.2014}
Clason,~C., Applegate,~P., and Holmlund,~P.: Modelling Late Weichselian evolution of the Eurasian ice sheets forced by surface meltwater-enhanced basal sliding,~J. Glaciol., 60, 29--40,
doi:\href{http://dx.doi.org/10.3189/2014jog13j037}{10.3189/2014jog13j037}, 2014.

\bibitem[{Cosma et~al.(2008)Cosma, Hendy, and Chang}]{Cosma.etal.2008}
Cosma,~T., Hendy,~I., and Chang,~A.: Chronological constraints on Cordilleran Ice Sheet glaciomarine sedimentation from core MD02-2496 off Vancouver Island (western Canada), Quaternary Sci. Rev., 27, 941--955,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2008.01.013}{10.1016/j.quascirev.2008.01.013}, 2008.

\bibitem[{Dansgaard et~al.(1993)Dansgaard, Johnsen, Clausen, Dahl-Jensen, Gundestrup, Hammer, Hvidberg, Steffensen, Sveinbj\"ornsdottir, Jouzel, and Bond}]{Dansgaard.etal.1993}
Dansgaard,~W., Johnsen,~S.~J., Clausen,~H.~B., Dahl-Jensen,~D., Gundestrup,~N.~S., Hammer,~C.~U., Hvidberg,~C.~S., Steffensen,~J.~P., Sveinbj\"ornsdottir,~A.~E., Jouzel,~J., and Bond,~G.: Evidence for general instability of past climate from a 250-kyr ice-core record, Nature, 364, 218--220,
doi:\href{http://dx.doi.org/10.1038/364218a0}{10.1038/364218a0}, data archived at the World Data Center for Paleoclimatology, Boulder, Colorado, USA., 1993.

\bibitem[{Davies et~al.(2011)Davies, Mix, Stoner, Addison, Jaeger, Finney, and Wiest}]{Davies.etal.2011}
Davies,~M.~H., Mix,~A.~C., Stoner,~J.~S., Addison,~J.~A., Jaeger,~J., Finney,~B., and Wiest,~J.: The deglacial transition on the southeastern Alaska Margin: Meltwater input, sea level rise, marine productivity, and sedimentary anoxia, Paleoceanography, 26, PA2223,
doi:\href{http://dx.doi.org/10.1029/2010pa002051}{10.1029/2010pa002051}, 2011.

\bibitem[{Davis and Mathews(1944)}]{Davis.Mathews.1944}
Davis,~N.~F.~G. and Mathews,~W.~H.: Four phases of glaciation with illustrations from Southwestern British Columbia,~J. Geol., 52, 403--413,
doi:\href{http://dx.doi.org/10.1086/625236}{10.1086/625236}, 1944.

\bibitem[{Dawson(1888)}]{Dawson.1888}
Dawson,~G.~M.: III. -- Recent observations on the glaciation of British Columbia and adjacent regions, Geol. Mag., 5, 347--350,
doi:\href{http://dx.doi.org/10.1017/s0016756800182159}{10.1017/s0016756800182159}, 1888.

\bibitem[{Demuro et~al.(2012)Demuro, Froese, Arnold, and Roberts}]{Demuro.etal.2012}
Demuro,~M., Froese,~D.~G., Arnold,~L.~J., and Roberts,~R.~G.: Single-grain OSL dating of glaciofluvial quartz constrains Reid glaciation in NW Canada to MIS 6, Quaternary Res., 77, 305--316,
doi:\href{http://dx.doi.org/10.1016/j.yqres.2011.11.009}{10.1016/j.yqres.2011.11.009}, 2012.

\bibitem[{Duk-Rodkin(1999)}]{Duk-Rodkin.1999}
Duk-Rodkin,~A.: Glacial limits map of Yukon Territory, Open File 3694, Geol. Surv. of Can., Ottawa, ON,
doi:\href{http://dx.doi.org/10.4095/210739}{10.4095/210739}, 1999.

\bibitem[{Duk-Rodkin et~al.(1996)Duk-Rodkin, Barendregt, Tarnocai, and Phillips}]{Duk-Rodkin.etal.1996}
Duk-Rodkin,~A., Barendregt,~R.~W., Tarnocai,~C., and Phillips,~F.~M.: Late Tertiary to late Quaternary record in the Mackenzie Mountains, Northwest Territories, Canada: stratigraphy, paleosols, paleomagnetism, and chlorine-36, Can.~J. Earth Sci., 33, 875--895,
doi:\href{http://dx.doi.org/10.1139/e96-066}{10.1139/e96-066}, 1996.

\bibitem[{Dyke(2004)}]{Dyke.2004}
Dyke,~A.~S.: An outline of North American deglaciation with emphasis
on central and northern Canada, in: Dev. Quaternary Sci., vol.~2,
edited by: Ehlers,~J. and Gibbard,~P.~L., Elsevier, Amsterdam, 373--424,
doi:\href{http://dx.doi.org/10.1016/S1571-0866(04)80209-4}{10.1016/S1571-0866(04)80209-4}, 2004.

\bibitem[{Dyke and Prest(1987)}]{Dyke.Prest.1987}
Dyke,~A.~S. and Prest,~V.~K.: Late wisconsinan and holocene history of the laurentide ice sheet, G{e}ogr. Phys. Quatern., 41, 237--263,
doi:\href{http://dx.doi.org/10.7202/032681ar}{10.7202/032681ar}, 1987.

\bibitem[{Dyke et~al.(2003)Dyke, Moore, and Robertson}]{Dyke.etal.2003}
Dyke,~A.~S., Moore,~A., and Robertson,~L.: Deglaciation of North America, Open File 1547, Geol. Surv. of Can., Ottawa, ON, 2003.

\bibitem[{Ehlers and Gibbard(2004)}]{Ehlers.Gibbard.2004}
Ehlers,~J. and Gibbard,~P.~L. (Eds.): Dev. Quaternary Sci., vol.~2, Elsevier, Amsterdam, 2004.

\bibitem[{Ehlers et~al.(2011)Ehlers, Gibbard, and Hughes}]{Ehlers.etal.2011}
Ehlers,~J., Gibbard,~P.~L., and Hughes,~P.~D. (Eds.):  Dev. Quaternary
Sci., vol.~15, Elsevier, Amsterdam, 2011.

\bibitem[{Fahnestock et~al.(2001)Fahnestock, Abdalati, Joughin, Brozena, and Gogineni}]{Fahnestock.etal.2001}
Fahnestock,~M., Abdalati,~W., Joughin,~I., Brozena,~J., and Gogineni,~P.: High geothermal heat flow, basal melt, and the origin of rapid ice flow in central greenland, Sience, 294, 2338--2342,
doi:\href{http://dx.doi.org/10.1126/science.1065370}{10.1126/science.1065370}, 2001.

\bibitem[{Friele and Clague(2002{\natexlab{a}})}]{Friele.Clague.2002}
Friele,~P.~A. and Clague,~J.~J.: Readvance of glaciers in the British Columbia Coast Mountains at the end of the last glaciation, Quatern. Int., 87, 45--58,
doi:\href{http://dx.doi.org/10.1016/s1040-6182(01)00061-1}{10.1016/s1040-6182(01)00061-1}, 2002{\natexlab{a}}.

\bibitem[{Friele and Clague(2002{\natexlab{b}})}]{Friele.Clague.2002a}
Friele,~P.~A. and Clague,~J.~J.: Younger Dryas readvance in Squamish river valley, southern Coast mountains, British Columbia, Quaternary Res., 21, 1925--1933,
doi:\href{http://dx.doi.org/10.1016/s0277-3791(02)00081-1}{10.1016/s0277-3791(02)00081-1}, 2002{\natexlab{b}}.

\bibitem[{Fulton(1967)}]{Fulton.1967}
Fulton,~R.~J.: Deglaciation studies in Kamloops region, an area of moderate relief, British Columbia, vol. 154 of Bull., Geol. Surv. of Can., Ottawa, ON,
doi:\href{http://dx.doi.org/10.4095/101467}{10.4095/101467}, 1967.

\bibitem[{Fulton(1991)}]{Fulton.1991}
Fulton,~R.~J.: A Conceptual model for growth and decay of the Cordilleran Ice Sheet, G{e}ogr. Phys. Quatern., 45, 281--286,
doi:\href{http://dx.doi.org/10.7202/032875ar}{10.7202/032875ar}, 1991.

\bibitem[{Golledge et~al.(2012)Golledge, Mackintosh, Anderson, Buckley, Doughty, Barrell, Denton, Vandergoes, Andersen, and Schaefer}]{Golledge.etal.2012}
Golledge,~N.~R., Mackintosh,~A.~N., Anderson,~B.~M., Buckley,~K.~M., Doughty,~A.~M., Barrell,~D.~J., Denton,~G.~H., Vandergoes,~M.~J., Andersen,~B.~G., and Schaefer,~J.~M.: Last Glacial Maximum climate in {N}ew {Z}ealand inferred from a modelled {S}outhern {A}lps icefield, Quaternary Res., 46, 30--45,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2012.05.004}{10.1016/j.quascirev.2012.05.004}, 2012.

\bibitem[{Herbert et~al.(2001)Herbert, Schuffert, Andreasen, Heusser, Lyle, Mix, Ravelo, Stott, and Herguera}]{Herbert.etal.2001}
Herbert,~T.~D., Schuffert,~J.~D., Andreasen,~D., Heusser,~L., Lyle,~M., Mix,~A., Ravelo,~A.~C., Stott,~L.~D., and Herguera,~J.~C.: Collapse of the California current during glacial maxima linked to climate change on land, Sience, 293, 71--76,
doi:\href{http://dx.doi.org/10.1126/science.1059209}{10.1126/science.1059209}, data archived at the World Data Center for Paleoclimatology, Boulder, Colorado, USA, 2001.

\bibitem[{Hidy et~al.(2013)Hidy, Gosse, Froese, Bond, and Rood}]{Hidy.etal.2013}
Hidy,~A.~J., Gosse,~J.~C., Froese,~D.~G., Bond,~J.~D., and Rood,~D.~H.: A latest Pliocene age for the earliest and most extensive Cordilleran Ice Sheet in northwestern Canada, Quaternary Res., 61, 77--84,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2012.11.009}{10.1016/j.quascirev.2012.11.009}, 2013.

\bibitem[{Hock(2003)}]{Hock.2003}
Hock,~R.: Temperature index melt modelling in mountain areas,~J. Hydrol., 282, 104--115,
doi:\href{http://dx.doi.org/10.1016/S0022-1694(03)00257-9}{10.1016/S0022-1694(03)00257-9}, 2003.

\bibitem[{Imbrie et~al.(1989)Imbrie, McIntyre, and Mix}]{Imbrie.etal.1989}
Imbrie,~J., McIntyre,~A., and Mix,~A.: Oceanic response to orbital forcing in the late quaternary: observational and experimental strategies, in: Climate and Geo-Sciences, edited by: Berger,~A., Schneider,~S., and Duplessy,~J., vol. 285 of NATO ASI Series C, Kluwer, Norwell, MA, 121--164,
doi:\href{http://dx.doi.org/10.1007/978-94-009-2446-8_7}{10.1007/978-94-009-2446-8\_7}, 1989.

\bibitem[{Ivy-Ochs et~al.(1999)Ivy-Ochs, Schluchter, Kubik, and Denton}]{Ivy-Ochs.etal.1999}
Ivy-Ochs,~S., Schluchter,~C., Kubik,~P.~W., and Denton,~G.~H.: Moraine
exposure dates imply synchronous Younger Dryas Glacier advances in the
European Alps and in the Southern Alps of New Zealand, Geogr. Ann. A, 81,
313--323,
doi:\href{http://dx.doi.org/10.1111/1468-0459.00060}{10.1111/1468-0459.00060},
1999.

\bibitem[{Jackson and Clague(1991)}]{Jackson.Clague.1991}
Jackson,~L.~E. and Clague,~J.~J.: The Cordilleran ice sheet: one hundred and fifty years of exploration and discovery, G{e}ogr. Phys. Quatern., 45, 269--280,
doi:\href{http://dx.doi.org/10.7202/032874ar}{10.7202/032874ar}, 1991.

\bibitem[{Jackson et~al.(1997)Jackson, Phillips, Shimamura, and Little}]{Jackson.etal.1997}
Jackson,~L.~E., Phillips,~F.~M., Shimamura,~K., and Little,~E.~C.: Cosmogenic $^{36}$Cl dating of the Foothills erratics train, Alberta, Canada, Geology, 25, 195,
doi:\href{http://dx.doi.org/10.1130/0091-7613(1997)025<0195:ccdotf>2.3.co;2}{10.1130/0091-7613(1997)025\textless0195:ccdotf\textgreater2.3.co;2}, 1997.

\bibitem[{James et~al.(2009)James, Gowan, Wada, and Wang}]{James.etal.2009}
James,~T.~S., Gowan,~E.~J., Wada,~I., and Wang,~K.: Viscosity of the
asthenosphere from glacial isostatic adjustment and subduction dynamics at
the northern Cascadia subduction zone, British Columbia, Canada,~J. Geophys.
Res., 114, B04405,
doi:\href{http://dx.doi.org/10.1029/2008jb006077}{10.1029/2008jb006077},
2009.

\bibitem[{Johnsen et~al.(1995)Johnsen, Dahl-Jensen, Dansgaard, and Gundestrup}]{Johnsen.etal.1995}
Johnsen,~S.~J., Dahl-Jensen,~D., Dansgaard,~W., and Gundestrup,~N.: Greenland palaeotemperatures derived from GRIP bore hole temperature and ice core isotope profiles, Tellus B, 47, 624--629,
doi:\href{http://dx.doi.org/10.1034/j.1600-0889.47.issue5.9.x}{10.1034/j.1600-0889.47.issue5.9.x}, 1995.

\bibitem[{Jouzel et~al.(2007)Jouzel, Masson-Delmotte, Cattani, Dreyfus, Falourd, Hoffmann, Minster, Nouet, Barnola, Chappellaz, Fischer, Gallet, Johnsen, Leuenberger, Loulergue, Luethi, Oerter, Parrenin, Raisbeck, Raynaud, Schilt, Schwander, Selmo, Souchez, Spahni, Stauffer, Steffensen, Stenni, Stocker, Tison, Werner, and Wolff}]{Jouzel.etal.2007}
Jouzel,~J., Masson-Delmotte,~V., Cattani,~O., Dreyfus,~G., Falourd,~S., Hoffmann,~G., Minster,~B., Nouet,~J., Barnola,~J.~M., Chappellaz,~J., Fischer,~H., Gallet,~J.~C., Johnsen,~S., Leuenberger,~M., Loulergue,~L., Luethi,~D., Oerter,~H., Parrenin,~F., Raisbeck,~G., Raynaud,~D., Schilt,~A., Schwander,~J., Selmo,~E., Souchez,~R., Spahni,~R., Stauffer,~B., Steffensen,~J.~P., Stenni,~B., Stocker,~T.~F., Tison,~J.~L., Werner,~M., and Wolff,~E.~W.: Orbital and millennial antarctic climate variability over the past 800\,000~years, Sience, 317, 793--796,
doi:\href{http://dx.doi.org/10.1126/science.1141038}{10.1126/science.1141038}, data archived at the World Data Center for Paleoclimatology, Boulder, Colorado, USA., 2007.

\bibitem[{Kaufman and Manley(2004)}]{Kaufman.Manley.2004}
Kaufman,~D.~S. and Manley,~W.~F.: Pleistocene maximum and late wisconsinan glacier extents across Alaska, {USA}, in: Dev. Quaternary Sci., vol.~2,
edited by: Ehlers,~J. and Gibbard,~P.~L., Elsevier, Amsterdam, 9--27,
doi:\href{http://dx.doi.org/10.1016/S1571-0866(04)80182-9}{10.1016/S1571-0866(04)80182-9}, 2004.

\bibitem[{Kleman(1994)}]{Kleman.1994}
Kleman,~J.: Preservation of landforms under ice sheets and ice caps, Geomorphology, 9, 19--32,
doi:\href{http://dx.doi.org/10.1016/0169-555x(94)90028-0}{10.1016/0169-555x(94)90028-0}, 1994.

\bibitem[{Kleman and Stroeven(1997)}]{Kleman.Stroeven.1997}
Kleman,~J. and Stroeven,~A.~P.: Preglacial surface remnants and Quaternary glacial regimes in northwestern Sweden, Geomorphology, 19, 35--54,
doi:\href{http://dx.doi.org/10.1016/s0169-555x(96)00046-3}{10.1016/s0169-555x(96)00046-3}, 1997.

\bibitem[{Kleman et~al.(1997)Kleman, H{\"a}ttestrand, Borgstr{\"o}m, and Stroeven}]{Kleman.etal.1997}
Kleman,~J., H{\"a}ttestrand,~C., Borgstr{\"o}m,~I., and Stroeven,~A.: Fennoscandian paleoglaciology reconstructed using a glacial geological inversion model,~J. Glaciol., 43, 283--299, 1997.

\bibitem[{Kleman et~al.(2006)Kleman, H{\"a}ttestrand, Stroeven, Jansson, De~Angelis, and Borgstr{\"o}m}]{Kleman.etal.2006}
Kleman,~J., H{\"a}ttestrand,~C., Stroeven,~A.~P., Jansson,~K.~N., De~Angelis,~H., and Borgstr{\"o}m,~I.: Reconstruction of palaeo-ice sheets -- inversion of their glacial geomorphological record, in: Glacier Science and Environmental Change, edited by: Knight,~P.~G., Blackwell, Malden, MA, 192--198,
doi:\href{http://dx.doi.org/10.1002/9780470750636.ch38}{10.1002/9780470750636.ch38}, 2006.

\bibitem[{Kleman et~al.(2008)Kleman, Stroeven, and Lundqvist}]{Kleman.etal.2008}
Kleman,~J., Stroeven,~A.~P., and Lundqvist,~J.: Patterns of quaternary ice sheet erosion and deposition in Fennoscandia and a theoretical framework for explanation, Geomorphology, 97, 73--90,
doi:\href{http://dx.doi.org/10.1016/j.geomorph.2007.02.049}{10.1016/j.geomorph.2007.02.049}, 2008.

\bibitem[{Kleman et~al.(2010)Kleman, Jansson, De~Angelis, Stroeven, H\"{a}ttestrand, Alm, and Glasser}]{Kleman.etal.2010}
Kleman,~J., Jansson,~K., De~Angelis,~H., Stroeven,~A., H\"{a}ttestrand,~C., Alm,~G., and Glasser,~N.: North American ice sheet build-up during the last glacial cycle, 115--21\,kyr, Quaternary Sci. Rev., 29, 2036--2051,
doi:\href{http://dx.doi.org/10.1016/j.quascirev.2010.04.021}{10.1016/j.quascirev.2010.04.021}, 2010.

\bibitem[{Kovanen(2002)}]{Kovanen.2002}
Kovanen,~D.~J.: Morphologic and stratigraphic evidence for Aller{\o}d and Younger Dryas age glacier fluctuations of the Cordilleran Ice Sheet, British Columbia, Canada and Northwest Washington,~USA, Boreas, 31, 163--184,
doi:\href{http://dx.doi.org/10.1111/j.1502-3885.2002.tb01064.x}{10.1111/j.1502-3885.2002.tb01064.x}, 2002.

\bibitem[{Kovanen and Easterbrook(2002)}]{Kovanen.Easterbrook.2002}
Kovanen,~D.~J. and Easterbrook,~D.~J.: Timing and extent of Aller{\o}d and Younger Dryas age (ca. 12\,500--10\,000 $^{14}$C~yr~BP) oscillations of the Cordilleran Ice Sheet in the Fraser Lowland, Western North America, Quaternary Res., 57, 208--224,
doi:\href{http://dx.doi.org/10.1006/qres.2001.2307}{10.1006/qres.2001.2307}, 2002.
